\section{Specific Requirements} \label{sec:spec_requirements}

%More details on all aspects in Section 2 if they can be  useful for the development team

\subsection{External Interface Requirements} \label{external}

\subsubsection{User Interface} \label{user_interface}

\subsubsection{Hardware Interfaces} \label{hw_interfaces}

\subsubsection{Software Interfaces} \label{sw_interfaces}

\subsubsection{Communication Interfaces} \label{comm_interfaces}

\subsection{Functional Requirements} \label{sec:funct_requirements}
In this section we explain all the functional requirements necessary to reach a specific goal. For each goal that was mentioned in the first section here we write its requirements.
\begin{itemize}
\item[\textbf{G1}]: 
\begin{itemize}
\item[--R1--] During the registration visitors can't choose an username already in use.
\item[--R2--] During the registration visitors can't choose an e-mail already in use.
\item[--R3--] During the registration visitors must insert valid credit card's information.
\item[--R4--] During the registration visitors must insert a valid driving license.
\item[--R5--] During the registration visitors must agree with the privacy conditions to use the system.
\end{itemize}

\item[\textbf{G2}]:
\begin{itemize}
\item[--R1--] The registration must be successfully completed.
\end{itemize}

\item[\textbf{G3}]:
\begin{itemize}
\item[--R1--] The user must be registered at the system.
\item[--R2--] In the log in form the user must insert the correct username.
\item[--R3--] In the log in form the user must insert the correct password.
\item[--R4--] If the visitor insert the wrong data, the system shows an error and return to the log in page.
\item[--R5--] If the user doesn't remember the password he can receive it trough a special command.
\end{itemize}

\item[\textbf{G4}]:
\begin{itemize}
\item[--R1--] The user must insert a valid address or give to the system his position.
\item[--R2--] All cars position must be knowed.
\item[--R3--] All cars are set as available or not.
\item[--R4--] The list of nearest cars is made trough calculate the distance between car and user's position.
\end{itemize}

\item[\textbf{G5}]:
\begin{itemize}
\item[--R1--] The user must be correctly logged in.
\item[--R2--] The user must select which car he wants.
\item[--R3--] The user must select only date and times valid for the reservation.
\end{itemize}

\item[\textbf{G6}]:
\begin{itemize}
\item[--R1--] The position of the user and the car must be the same.
\item[--R2--] The reservation must not be expired.
\item[--R3--] The system must recognize the correct car reserved by a specific user to unlock the correct one.
\end{itemize}

\item[\textbf{G7}]:
\begin{itemize}
\item[--R1--] The car's engine must ignites.
\item[--R2--] An amount of money per minute is set.
\item[--R3--] The final charge is based on the duration of the car use.
\end{itemize}

\item[\textbf{G8}]:
\begin{itemize}
\item[--R1--] There must be a display on the car that communicates with the system.
\item[--R2--] The charge is update every minute.
\end{itemize}

\item[\textbf{G9}]:
\begin{itemize}
\item[--R1--] It must be passed one hour from the registration.
\item[--R2--] Is applyed a fee of 1 euro to the user involved.
\item[--R3--] The reservation is deleted.
\end{itemize}

\item[\textbf{G10}]:
\begin{itemize}
\item[--R1--] The user must be correctly logged in.
\item[--R2--] The user must go to the reservation page.
\item[--R3--] Mustn't be passed one hour from the reservation.
\end{itemize}

\item[\textbf{G11}]:
\begin{itemize}
\item[--R1--] The reservation is correctly deleted by a user or it is expired. 
\item[--R2--] The car is set available in the list.

\end{itemize}

\item[\textbf{G12}]:
\begin{itemize}
\item[--R1--] A list of safe areas must be available to the user.
\item[--R2--] The car must be left in a safe area.
\item[--R3--] The user and all any passengers must exit from the car.
\end{itemize}

\item[\textbf{G13}]:
\begin{itemize}
\item[--R1--] The car must be used by a user.
\item[--R2--] Discounts are in a list where is defined all details.
\item[--R3--] In the car there is a sensor which counts how many people there are in the car, if they are three or more a discount is applied.
\item[--R4--] In the car there is a sensor which controls how many battery is empty, if it is no more than 50 per cent the system applied a discount.
\item[--R5--] If the user takes care to link the car to recharge the car he will have a discount.
\end{itemize}

\item[\textbf{G14}]:
\begin{itemize}
\item[--R1--] The car must have been recently used.
\item[--R2--] Most of 80 per cent of the battery is empty.
\item[--R3--] The car is left far away from a safe area.
\end{itemize}














\end{itemize}




\subsection{Performance Requirements} \label{sec:perf_requirements}

\subsection{Design Constraints} \label{sec:design_constr}

\subsubsection{Standards compliance} \label{std_compliance}

\subsubsection{Hardware limitations} \label{hw_limitations}

\subsubsection{etc...}

\subsection{Software System Attributes} \label{sec:sw_sys_attr}

\subsubsection{Reliability} \label{reliability}

\subsubsection{Availability} \label{availability}

\subsubsection{Security} \label{security}

\subsubsection{Maintainability} \label{maintainability}

\subsubsection{Portability} \label{portability}

\subsection{Other Requirements} \label{other}
